Paradigms in Physics 2.0

### 2017-06-29 paper.tex
a couple of citations added

\subsection{Computational lab}
Over the last six years, we have been developing a 1-credit
computational laboratory course that accompanies the \emph{Paradigm} courses.  We
chose to require this course, while removing a requirement for a
lower-division 3-credit course in computational physics.  This
lower-division course was challenging to teach, since it always had a
mix of lower- and upper-division students, with very different skill
levels and needs.  Transfer students now take computation alongside
the non-transfer students. The course is taught in a laboratory setting using pair
programming to help new programmers to learn. \davidsays{CITE!}

@@

\paragraph{Physics of Contemporary Challenges}
In this course we prepare students to
apply physics concepts and physical reasoning skills to sustainable
energy issues, climate change mechanisms, space exploration and
puzzles in fundamental physics. These ``real-world'' topics are chosen
for either the societal need (energy and climate), and/or the human
need to explore (space and fundamental physics). By prioritizing
inclusion of the most engaging challenges, we aim to attract and
retain as many potential physics majors as possible.
\davidsays{Add in reference and note?}

>>>>

\subsection{Computational lab}
Over the last six years, we have been developing a 1-credit
computational laboratory course that accompanies the \emph{Paradigm} courses.  We
chose to require this course, while removing a requirement for a
lower-division 3-credit course in computational physics.  This
lower-division course was challenging to teach, since it always had a
mix of lower- and upper-division students, with very different skill
levels and needs.  Transfer students now take computation alongside
the non-transfer students. The course is taught in a laboratory setting using pair
programming~\cite{mcdowell2006pair} to help new programmers to learn.

@@

\paragraph{Physics of Contemporary Challenges}
In this course we prepare students to
apply physics concepts and physical reasoning skills to sustainable
energy issues, climate change mechanisms, space exploration and
puzzles in fundamental physics. These ``real-world'' topics are chosen
for either the societal need (energy and climate), and/or the human
need to explore (space and fundamental physics). By prioritizing
inclusion of the most engaging challenges, we aim to attract and
retain as many potential physics majors as 
possible~\cite{kramer2016gathering}.
